# 1 Section Left

``` {r}
BlastOffPaste <- function(x) {
  ans <- paste("5,","4,","3,","2,","1,", "Blastoff!", collapse = "/n")
  return(cat(ans))
}
BlastOffPaste(5)
```


``` {r}
blastOffFor <- function(x) {
  count <- 0
  ans <- c()
  for(k in x:1){
    count <- k
    ans <- paste(ans, count)
    }
  newans <- paste(ans, "BlastOff!", collapse="")
  return(newans)
  }
  
blastOffFor(5)
```


# Cant finish
``` {r}
blastWhile <- function(x) {
  ans <- c()
  while (x > 0) {
    ans <- c(ans, x)
    x <-x-1
  }
  newans <- paste(ans, "BlastOff!", collapse="")
  return(newans)
  }
blastWhile(5)
```

``` {r}
blastOffRep <- function(x) {
  time <- 5
  repeat {
    x <- cat(time, " ")
    time <- time - 1
    if (time < 1) 
        break
         }
  
  return(cat(paste(x, "Blastoff!", sep = "")))
}
blastOffRep(5)
```

``` {r}
testLatency <- function(N) {
  result <- rep(NA, N)
  readline("Ready?")
  
  for ( k in 1:20) {
    
    start <- Sys.time()
    readline("Press return:")
    end <- Sys.time()
    total <- as.numeric(end - start)
    cat(rep("\n", 1))
    result[k] <- total
    Sys.sleep(runif(1,1,5))
    }
  return(result)
  }
```

``` {r}
Elaboration <- function(n) {
  result <- rep(NA, N)
  readline("ready")
  
  for ( k in 1:n) {
    cat(rep("\n",20))
    Sys.Sleep(pauses[k])
    start <- Sys.time()
    scramble <- strsplit("random", split=character(0))
    inpuut <- scramble[[1]][sample(nchar("random"):1)]
    inpuut <- paste(inpuut, collapse="")
    val <- readline(paste("Type in:", inpuut, " "))
    while (inpuut != val){
      val <- readline(paste("Try again: "))
    }
    end <- Sys.time()
    total <- as.numeric(end - start)
    cat(rep("\n", 1))
    result[k] <- total
    Sys.sleep(runif(1,1,5))
    }
  return(result)
}

