# October 1, 2013

## Reverser

Reverses the order from the last written element to the first written element, so the last element written is first and the first element written is last.


## Test Statements
```{r}
reverser <- function(x) {
    newFunc = strsplit(x, split = "")
    ans = newFunc[[1]][1:nchar(x)]
    return(rev(ans))
  }
   reverser("black")
```


# Scrambler

Input is a vector, the output is a the vector but the elements in a random order.


## Test Statements
``` {r}
scrambler <- function(x) {
  newFunc = strsplit(x, split = "")
  ans = newFunc[[1]][1:nchar(x)]
  return(sample(ans))  
}
scrambler("seven")
```

#VowelBleeper

```{r}
vowelsOut <- function(x) {
  ans = gsub("[aeiou]", "*", x)
  return(ans)
  }
vowelsOut("onomonopeia")
```

# L33t

```{r}
L33t <- function(x) {
  newFunc = gsub("e", "3", x)
  newFunc1 = gsub("o", "0", newFunc)
  newFunc2 = gsub("s", "5", newFunc1)
  newFunc3 = gsub("g", "9", newFunc2)
  
  return(newFunc3)
  }
L33t("eosgeosghheosg")
```

# Substituion Cypher

```{r} # same as L33t, but longer, every letter is replaced by only one other letter
subCypher <- function(x){
  
}